### 2016-07-04 ch03-lrm/nonparametric.tex
Add more historical references in Ch3

The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
However, obtaining a good non-parametric \gls{FRF} from a measured input-output data set can be challenging due to the presence of noise, leakage and measurement time limitations to observe lightly-damped dynamics well.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.

>>>>

The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
However, obtaining a good non-parametric \gls{FRF} from a measured input-output data set can be challenging due to the presence of noise, leakage and measurement time limitations to observe lightly-damped dynamics well.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012,Bendat2010,Bendat1993,Jenkins1968,Box2008,Bendat1978,Blackman1959,}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010,White1969}, among others.
